---
title: "infographics - Workshop 1 (Sept 2021)"
author: "Natalie Thurlby"
date: "9/30/2021"
output: html_document
---

This document creates the info-graphics from Data Hazards Workshop 1 - Sept 2021 - academic focus.
These info-graphics visualise things like how many people found the hazards useful.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(waffle)
```
## Read in and clean data

### Data provenance
The data is stored in a private folder called `data`, within the analysis folder. Data can be downloaded from [this](https://uob.sharepoint.com/:f:/r/teams/grp-ethicaldatascience/Shared%20Documents/Data%20Hazards/Results?csf=1&web=1&e=6pvo8u) SharePoint folder, for researchers working on the project only (at time of writing Natalie and Nina).

The data was collected through a series of surveys via wualtrics, for which the exact questions can be seen on the [Data Hazards project OSF page](https://osf.io/3fv7t/).

### Read in data

```{r cars}
survey_data <- read_csv('data/data-hazards-workshop-21-sept-2021.csv')
```
### Rename labels
```{r}
survey_data <- rename(survey_data, 
       Name=Q28, 
       AttendeeType=Q27, 
       ProjOwner=`Proj Title`, 
       HazardsPre=`Hazards Pre 1`, 
       HazardsComments1=`Hazards Comments`,
       HazardsPost=`Hazards Post 1`,
       HazardsComments2=Q18,
       Clarity=Q20,
       Ease=Q24,
       UsefulHazards=Q21,
       UsefulDiscussion=Q26,
       Learning=Q23,
       OverallHazards=Q27_1,
       OverallWorkshop=Q28_1,
       EncourageParticipation=Q29,
       )
```

### Data cleaning

Remove first row and use as a lookup for actual wording of questions
```{r}
question_wording <- survey_data[1,]
survey_data <- survey_data[-1,]
```

## Plots
To create the pictograms, I followed [this tutorial](https://rud.is/rpubs/building-pictograms.html) as a guide.

```{r}
```

```{r}
extrafont::font_import('~/Downloads/fontawesome-free-5.15.4-web/', prompt=FALSE)
```


### How useful did you think the Data Hazards were for exploring potential downfalls of data science projects?
```{r}
qscale <- c("1"="Very Useful", 
           "2"="Useful", 
           "3"="Neutral", 
           "4"="Not useful", 
           "5"="Not useful at all")
text <- question_wording$UsefulHazards
data <- tibble(survey_data$UsefulHazards)
#data$qscale = qscale[data]
qscale[data]
i```
```{r pressure, echo=FALSE}
# TODO: Change format of data so that it works in the geom_waffle
#ggplot(survey_data, aes(fill=UsefulHazards, values=UsefulHazards)) +
#  waffle::geom_waffle() 
ggplot(xdf, aes(fill=vals)) +
  waffle::geom_waffle() 
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
